### 2015-06-01 Dissertation/abstract.tex
Formatting from Jared
Removed "very" and cleaned up some related text

%%% Abstract:
\thispagestyle{empty} \setcounter{page}{2}
\begin{doublespace}
\begin{centering}
ABSTRACT\\ %
\MyTitle\\ %
By \\ %
Brian W. Goldman\\ %
\ \\
\end{centering}

@@

P3 can be further improved by specializing to the gray-box domain, which includes
partial solution evaluation and known, limited, non-linear relationships between variables.
This Gray-Box P3 leverages the Hamming-Ball Hill Climber, an exceptionally efficient
form of local search, as well as a novel method for performing crossover using the
known variable interactions. In doing so Gray-Box P3 is able to find the global
optimum to very large problems in seconds, improving over Black-Box P3 by up to
two orders of magnitude.
\end{doublespace}
\newpage

>>>>

%%% Abstract:
\thispagestyle{empty} \setcounter{page}{2}
\begin{doublespace}
\begin{centering}
ABSTRACT\\ %
\MyTitle\\ %
By \\ %
Brian W. Goldman\\ %
\end{centering}

@@

P3 can be further improved by specializing to the gray-box domain, which includes
partial solution evaluation and known, limited, non-linear relationships between variables.
This Gray-Box P3 leverages the Hamming-Ball Hill Climber, an exceptionally efficient
form of local search, as well as a novel method for performing crossover using the
known variable interactions. In doing so Gray-Box P3 is able to find the global
optimum of large problems in seconds, improving over Black-Box P3 by up to
two orders of magnitude.
\end{doublespace}
\newpage

### 2015-06-01 Dissertation/chapter-benchmarking.tex
Removed "very" and cleaned up some related text

To assess wall clock performance we provide Figure~\ref{fig-seconds-to-success}.
Similar to Figure~\ref{fig-evals-to-success}, each point represents the median
of 100 runs, with unsuccessful runs treated as slower than successful runs.
\begin{comment}
In total these runs
took over 6 computing years to complete. We were therefore forced to use
diverse hardware potentially running multiple processes in parallel.
As such these timings should be considered very skeptically as a number
of sources may contribute to biased error in the results. However, due to
the size of the dataset and the general regularity in the results some general conclusions
can still be made.
\end{comment}
These results were collected using 2.5GHz Intel Xeon E5-2670v2 processors.

>>>>

To assess wall clock performance we provide Figure~\ref{fig-seconds-to-success}.
Similar to Figure~\ref{fig-evals-to-success}, each point represents the median
of 100 runs, with unsuccessful runs treated as slower than successful runs.
These results were collected using 2.5GHz Intel Xeon E5-2670v2 processors.

### 2015-06-01 Dissertation/chapter-comparison_algorithms.tex
Removed "very" and cleaned up some related text

In order to fully understand the effectiveness of P3, we compare it with five advanced algorithms which
have related features to P3. The Random Restart Hill Climber defined by ~\cite{goldman:2014:p3} was chosen as an efficient form of repeated
local search. As P3 combines this hill climber with crossover,
comparing with local search alone shows the advantages of P3's overall approach.
The $1+(\lambda, \lambda)$ algorithm~\citep{doerr:2013:lambdalambda} is the current best theory supported simple genetic algorithm
and its method of crossover is in some sense a macro-mutation just as in P3. hBOA and Parameter-less
hBOA are advanced model building search techniques which are very effective at learning complex
problem structure, designed to achieve similar goals as P3's linkage learning but using very different
methods. Finally LTGA represents the current state-of-the-art in black-box search and is the origin
of P3's linkage learning and crossover methods.

@@

Like other model based techniques, hBOA has very few parameters. There is no mutation or crossover,
and modeling does not rely on any explicit parameters. Solution selection, generation, and replacement
are all derived from the population size, which must be set by the user.

@@

Figure~\ref{fig-pop-sizes} shows the results from performing bisection. In general hBOA
required population sizes which were at least an order of magnitude larger than LTGA. Due to
runtime and memory overhead, finding the optimal value for hBOA was much less tractable than LTGA
for moderate to large problem sizes. LTGA's population size also grew significantly slower
than hBOA's as problem size increased, especially on the two Trap problems and Rastrigin.
Both algorithms were very ineffective on MAX-SAT, neither able to tune to problems sizes over 60 bits.
This is likely due to the fact that some randomly generated MAX-SAT landscapes are very flat
and highly deceptive~\citep{rana:1998:gamaxsat}.

>>>>

In order to fully understand the effectiveness of P3, we compare it with five advanced algorithms which
have related features to P3. The Random Restart Hill Climber defined by ~\cite{goldman:2014:p3} was chosen as an efficient form of repeated
local search. As P3 combines this hill climber with crossover,
comparing with local search alone shows the advantages of P3's overall approach.
The $1+(\lambda, \lambda)$ algorithm~\citep{doerr:2013:lambdalambda} is the current best theory supported simple genetic algorithm
and its method of crossover is in some sense a macro-mutation just as in P3. hBOA and Parameter-less
hBOA are advanced model building search techniques which are effective at learning complex
problem structure, designed to achieve similar goals as P3's linkage learning but using very different
methods. Finally LTGA represents the current state-of-the-art in black-box search and is the origin
of P3's linkage learning and crossover methods.

@@

Like other model based techniques, hBOA has few parameters. There is no mutation or crossover,
and modeling does not rely on any explicit parameters. Solution selection, generation, and replacement
are all derived from the population size, which must be set by the user.

@@

Figure~\ref{fig-pop-sizes} shows the results from performing bisection. In general hBOA
required population sizes which were at least an order of magnitude larger than LTGA. Due to
runtime and memory overhead, finding the optimal value for hBOA was much less tractable than LTGA
for moderate to large problem sizes. LTGA's population size also grew significantly slower
than hBOA's as problem size increased, especially on the two Trap problems and Rastrigin.
Both algorithms were ineffective on MAX-SAT, with neither able to tune to problems sizes over 60 bits.
This is likely due to the fact that some randomly generated MAX-SAT landscapes are quite flat
and highly deceptive~\citep{rana:1998:gamaxsat}.

### 2015-06-01 Dissertation/chapter-conclusions.tex
Removed "very" and cleaned up some related text

P3's quality is due to a number of desirable traits. First, mixing local search with model based
crossover lets search focus on properly mixing high quality solutions. Second, by adding diversity only
as necessary P3 tends to use the minimal amount of random initialization, unlike other techniques which must
overcompensate with larger population sizes on single instance problems and consider the worst instance
when solving problem classes. Third, by heavily exploiting existing diversity before adding more P3 is able
to reach high quality intermediate fitnesses quickly without prematurely converging. Fourth, the very
nature of the pyramid's shape allows search to preserve a desirable proportion of diversity at
each fitness level, similar to a generational model using a decreasing population size.

>>>>

P3's quality is due to a number of desirable traits. First, mixing local search with model based
crossover lets search focus on properly mixing high quality solutions. Second, by adding diversity only
as necessary P3 tends to use the minimal amount of random initialization, unlike other techniques which must
overcompensate with larger population sizes on single instance problems and consider the worst instance
when solving problem classes. Third, by heavily exploiting existing diversity before adding more P3 is able
to reach high quality intermediate fitnesses quickly without prematurely converging. Fourth, the
nature of the pyramid's shape allows search to preserve a desirable proportion of diversity at
each fitness level, similar to a generational model using a decreasing population size.

### 2015-06-01 Dissertation/chapter-gray-box-benchmarking.tex
Removed "very" and cleaned up some related text

For all sizes of both problems, Gray-Box P3 was the fastest to reach the best fitness. On
Nearest Neighbor NKq the improvement is very significant, with no alternative finishing within
two orders of magnitude. On its largest successful problem size, the mean time to completion for
Black-Box P3 was 375 times slower than Gray-Box P3. Using the Mann-Whitney test to compare their run times
results in $p < 10^{-16}$. This is especially impressive considering
previous work has shown Black-Box P3 is faster to reach the global optimum than other leading black-box
methods~\cite{goldman:2015:fastp3}. Applying regression, we estimate that Black-Box P3's time to global optimum
on Nearest Neighbor NKq is \BigO{N^{2.75}} while Gray-Box P3's is \BigO{N^{1.98}}.

@@

Somewhat surprising is the difference in behavior between the polynomially solvable problems
and Unrestricted NKq. While Black-Box P3 performed very well in the former, it was the least
successful in the latter. The optimal radius for Gray-Box P3 also shifted from 1 to 2.
A potential explanation is that in both Ising Spin Glass
and Nearest Neighbor NKq the number of unique variables $r$
or fewer steps away from a given variable is significantly lower than the worst case. This explains why on Unrestricted NKq
even moderately high $r$ values hit our memory limit.
For Black-Box P3 this may also be causing increased difficulty in linkage learning as variables
become indirectly dependent on much larger sets. Furthermore, Black-Box
P3 may be benefiting from an increased rate of duplicate dependencies on Nearest Neighbor NKq
not present in Unrestricted NKq.

>>>>

For all sizes of both problems, Gray-Box P3 was the fastest to reach the best fitness. On
Nearest Neighbor NKq the improvement is substantial, with no alternative finishing within
two orders of magnitude. On its largest successful problem size, the mean time to completion for
Black-Box P3 was 375 times slower than Gray-Box P3. Using the Mann-Whitney test to compare their run times
results in $p < 10^{-16}$. This is especially impressive considering
previous work has shown Black-Box P3 is faster to reach the global optimum than other leading black-box
methods~\cite{goldman:2015:fastp3}. Applying regression, we estimate that Black-Box P3's time to global optimum
on Nearest Neighbor NKq is \BigO{N^{2.75}} while Gray-Box P3's is \BigO{N^{1.98}}.

@@

Somewhat surprising is the difference in behavior between the polynomially solvable problems
and Unrestricted NKq. While Black-Box P3 performed well in the former, it was the least
successful in the latter. The optimal radius for Gray-Box P3 also shifted from 1 to 2.
A potential explanation is that in both Ising Spin Glass
and Nearest Neighbor NKq the number of unique variables $r$
or fewer steps away from a given variable is significantly lower than the worst case. This explains why on Unrestricted NKq
even moderately high $r$ values hit our memory limit.
For Black-Box P3 this may also be causing increased difficulty in linkage learning as variables
become indirectly dependent on much larger sets. Furthermore, Black-Box
P3 may be benefiting from an increased rate of duplicate dependencies on Nearest Neighbor NKq
not present in Unrestricted NKq.

### 2015-06-01 Dissertation/chapter-graybox.tex
Removed "very" and cleaned up some related text

\chapter{New Problem Domain: Gray-Box Optimization}
\label{chap-graybox}
All of the work presented so far has focused on the black-box optimization
domain. These problems are characterized by a complete lack of available
problem specific information. All the algorithm has to perform search
is a ``black-box'' which measures the quality of arbitrary proposed
solutions. Optimizers which are successful in this domain are very general
as there are minimal requirements to apply them to a new problem.

@@

\section{Problems in this domain}
To understand the types of problems in this domain, lets first examine
a very simple artificial problem we'll call 3-Equal. The quality
of a solution is determined by how often three consecutive bits are set
to the same value. As a result the maximum fitness is $N$ (all zero or all one) and the minimum fitness
is 0.

>>>>

\chapter{New Problem Domain: Gray-Box Optimization}
\label{chap-graybox}
All of the work presented so far has focused on the black-box optimization
domain. These problems are characterized by a complete lack of available
problem specific information. All the algorithm has to perform search
is a ``black-box'' which measures the quality of arbitrary proposed
solutions. Optimizers which are successful in this domain generalize well
as there are minimal requirements to apply them to a new problem.

@@

\section{Problems in this domain}
To understand the types of problems in this domain, lets first examine
a simple artificial problem we'll call 3-Equal. The quality
of a solution is determined by how often three consecutive bits are set
to the same value. As a result the maximum fitness is $N$ (all zero or all one) and the minimum fitness
is 0.

### 2015-06-01 Dissertation/chapter-internal.tex
Removed "very" and cleaned up some related text

While analysis of optimization speed is useful from a practitioner standpoint, doing so provides very
little insight into algorithm behavior. To better understand how P3 works in detail we present here
a look at some internal features specific to P3.

@@

This behavior is rooted in the peculiar nature
of this landscape.
After local search, all traps in all solutions have a total
number of 1 bits equal to either 0, 1, 3, 5, or 7 as these correspond to the local
optima when using $k=7$ and $s=2$. Crossover is very likely to overcome the
two bit plateaus, and as a result solutions in the second level generally do not
contain the lowest fitness local optima (5 bits set) and the third
level has very few traps set to the next worst local optima (3 bits set). As a result,
solutions which reach the third level can only be improved by replacing the deceptive
local optima (0 and 1 bits set) with the global optimum (7 bits set).
The global optimum is very rare in the population, and with 8 ways to represent local optima
linkage learning is inaccurate. Therefore it is very unlikely for crossover to be successful,
meaning few solutions will be added to the fourth level. Solutions that do improve by
definition must have a higher frequency of optimal trap settings, meaning level four's model
will be more accurate and donations are more likely to contain optimal trap values.
Thus the level size and crossover success rates increase after contracting around level four.

>>>>

While analysis of optimization speed is useful from a practitioner standpoint, doing so provides
little insight into algorithm behavior. To better understand how P3 works in detail we present here
a look at some internal features specific to P3.

@@

This behavior is rooted in the peculiar nature
of this landscape.
After local search, all traps in all solutions have a total
number of 1 bits equal to either 0, 1, 3, 5, or 7 as these correspond to the local
optima when using $k=7$ and $s=2$. Crossover easily overcomes the
two bit plateaus, and as a result solutions in the second level generally do not
contain the lowest fitness local optima (5 bits set) and the third
level has few traps set to the next worst local optima (3 bits set). As a result,
solutions which reach the third level can only be improved by replacing the deceptive
local optima (0 and 1 bits set) with the global optimum (7 bits set).
The global optimum is rare in the population, and with 8 ways to represent local optima
linkage learning is inaccurate. Therefore it is unlikely for crossover to be successful,
meaning few solutions will be added to the fourth level. Solutions that do improve by
definition must have a higher frequency of optimal trap settings, meaning level four's model
will be more accurate and donations are more likely to contain optimal trap values.
Thus the level size and crossover success rates increase after contracting around level four.

### 2015-06-01 Dissertation/chapter-problems.tex
More hypens for black-box and gray-box
Removed "very" and cleaned up some related text

%%%%%%%%%%%%%%%%%% Randomly Generated %%%%%%%%%%%%%%%%%%%%%%
\section{Randomly Generated Problem Classes}
While well defined landscapes can provide specific insights into how an algorithm works,
their static nature can be misleading. Specifically, algorithm quality might
be very fragile such that it is only effective at searching well behaved landscapes. A more realistic
test of an algorithm's black box effectiveness is to work with randomly generated instances
drawn from a problem class. When tested over a sufficiently large sample it is then possible
to draw more general conclusions about the algorithms effectiveness. The challenge with these
landscapes is determining the global optimum to gauge if an algorithm was successful.

>>>>

%%%%%%%%%%%%%%%%%% Randomly Generated %%%%%%%%%%%%%%%%%%%%%%
\section{Randomly Generated Problem Classes}
While well defined landscapes can provide specific insights into how an algorithm works,
their static nature can be misleading. Specifically, algorithm quality might
be so fragile that it is only effective at searching well behaved landscapes. A more realistic
test of an algorithm's black-box effectiveness is to work with randomly generated instances
drawn from a problem class. When tested over a sufficiently large sample it is then possible
to draw more general conclusions about the algorithms effectiveness. The challenge with these
landscapes is determining the global optimum to gauge if an algorithm was successful.

### 2015-06-01 Dissertation/chapter-proposed.tex
Removed "very" and cleaned up some related text

\chapter{Proposed Research}
The Parameter-less Population Pyramid (P3) was shown to be very effective in Chapter~\ref{chap-benchmarking}
when applied to black-box optimization. Some of this effectiveness in due to P3's integration of
efficient local search and its ability to automatically detect and exploit variable epistasis.
In Chapter~\ref{chap-graybox} we presented the gray-box domain, which contains many interesting
real world problems, and the improvements that can be made to local search in this domain.
This presents the following questions:

@@

Current research on these gray-box methods have been very preliminary: a single size of a single problem class using
a single $r$, $k$, and $c$. To fully understand how to effectively perform search in this new domain, much more extensive testing
is necessary.

>>>>

\chapter{Proposed Research}
The Parameter-less Population Pyramid (P3) was shown to be effective in Chapter~\ref{chap-benchmarking}
when applied to black-box optimization. Some of this effectiveness in due to P3's integration of
efficient local search and its ability to automatically detect and exploit variable epistasis.
In Chapter~\ref{chap-graybox} we presented the gray-box domain, which contains many interesting
real world problems, and the improvements that can be made to local search in this domain.
This presents the following questions:

@@

Current research on these gray-box methods have been preliminary: a single size of a single problem class using
a single $r$, $k$, and $c$. To fully understand how to effectively perform search in this new domain, much more extensive testing
is necessary.

### 2015-06-01 Dissertation/chapter-understanding.tex
Removed "very" and cleaned up some related text

\chapter{Understanding When P3 Excels}
The ruggedness and high dimensionality of most interesting landscapes makes them very challenging
to visualize or otherwise understand. However, doing so can be very helpful in
understanding the difficulty of a problem, and how best to design algorithms to deal
with those difficulties. Conversely, understanding the characteristics which favor
existing algorithms can help future researchers choose the algorithm which is
most likely to perform well on their problem. To further this end, we shall
explore the landscapes used in previous sections in an attempt to understand
what makes a landscape easy for P3 to solve.

@@

\subsection{Looking at Problems}
In comparison to the randomly generated problem instances of Nearest Neighbor NKQ and Ising Spin Glass,
Deceptive Trap and Deceptive Step Trap have very comprehensible landscapes. Therefore, these problems represent
a good place to begin understanding what ``big valley'' plots are showing. Figure~\ref{fig-valley-trap} shows
how the local optima in each of these problems are distributed.

@@

The Deceptive Trap problem has very few local optima, each of which actually
provide very little deception in terms of ``big valley'' properties. Given any two local optima, the one
closer to the global optimum in fitness is also always closer to the global optimum in representation space.
This makes sense as the worst local optimum contains all 0s, and each fitness improvement beyond that involves
converting an entire trap to 1s, with the global optimum being all 1s. As a result, we should expect P3's method
of elitist mixing to produce solutions which are progressively more and more similar to the global optimum until
it is finally found.

@@

Figure~\ref{fig-valley-nn} shows how the local optima are distributed for Nearest Neighbor NKQ. Unlike the trap problems,
Nearest Neighbor NKQ exhibits a very traditional big valley shape. Increasing the radius of the local optima significantly
reduces the total number of local optima, with those optima generally more similar to the global optima in both representation
space and quality. Together this suggests that Nearest Neighbor NKQ is a good candidate for selection based methods like P3. Also,
due to the general regularity and frequency of local optima, it may not be necessary to increase the radius in order to quickly find
the global optimum.

@@

Similar to Unrestricted NKQ, the MAXSAT instance shown in Figure~\ref{fig-valley-sat} suggests selection can be very misleading.
There is almost a negative correlation between fitness difference from the global optimum and representation distance from the
global optimum. As before, this problem is not solved by increasing the radius of the local optima.
This may explain why methods like LTGA and hBOA, which extensively rely on selection,
scale so poorly when tested on this problem. P3's comparative success may therefore be the result of the random restart hill climber
eventually finding a solution in the correct area of the search space, with crossover finding the global optimum mostly by chance.

@@

Gray-Box P3's progression on Deceptive Step Trap, shown in Figure~\ref{fig-level-dst}, follows directly from our expectations.
The local optima found using only hill climbing and stored in level 0 are quite poor and very far from the global optima.
The first application of crossover dramatically improves their quality. However, this improvement is likely just overcoming
the fitness plateaus, as solutions are actually being moved away from the global optimum. Subsequent levels store solutions
which are generally closer to the global optimum in both fitness and representation space. This change means that at higher
levels the frequency of traps being set to the global optima increases, resulting in better model building and better donation quality.

@@

Gray-Box P3's progression on Ising Spin Glass, shown in Figure~\ref{fig-level-is}, is much more well behaved than on Unrestricted
NKQ. As has been typical, each application of crossover results in improved fitness, with the largest gains between the first few levels.
When approaching higher qualities these improvements also begin to translate into increased representational similarity to the global optimum.
However, as discussed previously for this problem, we again see evidence for a large number of very diverse solutions with the second best
fitness. These solutions can be over 1000 bits different from the eventual best found solution. Increasing the radius of the hill climber
does not seem to significantly overcome this issue.

@@

Figure~\ref{fig-level-sat} shows that Gray-Box P3 acts more similarly on MAX-SAT to Unrestricted NKQ than any of the other problems. Again there
appears to be deceptive local optima between 500 and 1000 bits away from the nearest improving solution. Again a single solution appears
to be the ancestor of all of the solutions near the best found. This suggests that similar to Unrestricted NKQ, Gray-Box P3 will have a
very hard time finding the global optimum on MAX-SAT.

In general it appears that the problems which have polynomial time solutions (Deceptive Step Trap, Nearest Neighbor NKQ, 2D Ising Spin Glass)
share a similar behavior of selection leading to the global optimum. However, the NP-Hard problems (Unrestricted NKQ, MAX-SAT) seem to contain
very large amounts of higher order deception, making them challenging for selection based methods. This relationship warrants further investigation
into other NP-Hard problems to determine if the repeated selection found in P3 and other evolutionary computation methods are able to overcome
this deception. One potential avenue for improvement to P3 may also be a method for dealing with this issue. For instance, it may be beneficial to
explicitly partition solutions when this deceptive behavior is observed.

>>>>

\chapter{Understanding When P3 Excels}
The ruggedness and high dimensionality of most interesting landscapes makes them challenging
to visualize or otherwise understand. However, doing so can be helpful in
understanding the difficulty of a problem, and how best to design algorithms to deal
with those difficulties. Conversely, understanding the characteristics which favor
existing algorithms can help future researchers choose the algorithm which is
most likely to perform well on their problem. To further this end, we shall
explore the landscapes used in previous sections in an attempt to understand
what makes a landscape easy for P3 to solve.

@@

\subsection{Looking at Problems}
In comparison to the randomly generated problem instances of Nearest Neighbor NKQ and Ising Spin Glass,
Deceptive Trap and Deceptive Step Trap have comprehensible landscapes. Therefore, these problems represent
a good place to begin understanding what ``big valley'' plots are showing. Figure~\ref{fig-valley-trap} shows
how the local optima in each of these problems are distributed.

@@

The Deceptive Trap problem has few local optima, each of which actually
provide little deception in terms of ``big valley'' properties. Given any two local optima, the one
closer to the global optimum in fitness is also always closer to the global optimum in representation space.
This makes sense as the worst local optimum contains all 0s, and each fitness improvement beyond that involves
converting an entire trap to 1s, with the global optimum being all 1s. As a result, we should expect P3's method
of elitist mixing to produce solutions which are progressively more and more similar to the global optimum until
it is finally found.

@@

Figure~\ref{fig-valley-nn} shows how the local optima are distributed for Nearest Neighbor NKQ. Unlike the trap problems,
Nearest Neighbor NKQ exhibits a traditional big valley shape. Increasing the radius of the local optima significantly
reduces the total number of local optima, with those optima generally more similar to the global optima in both representation
space and quality. Together this suggests that Nearest Neighbor NKQ is a good candidate for selection based methods like P3. Also,
due to the general regularity and frequency of local optima, it may not be necessary to increase the radius in order to quickly find
the global optimum.

@@

Similar to Unrestricted NKQ, the MAXSAT instance shown in Figure~\ref{fig-valley-sat} suggests selection can be misleading.
There is almost a negative correlation between fitness difference from the global optimum and representation distance from the
global optimum. As before, this problem is not solved by increasing the radius of the local optima.
This may explain why methods like LTGA and hBOA, which extensively rely on selection,
scale so poorly when tested on this problem. P3's comparative success may therefore be the result of the random restart hill climber
eventually finding a solution in the correct area of the search space, with crossover finding the global optimum mostly by chance.

@@

Gray-Box P3's progression on Deceptive Step Trap, shown in Figure~\ref{fig-level-dst}, follows directly from our expectations.
The local optima found using only hill climbing and stored in level 0 are quite poor and far from the global optima.
The first application of crossover dramatically improves their quality. However, this improvement is likely just overcoming
the fitness plateaus, as solutions are actually being moved away from the global optimum. Subsequent levels store solutions
which are generally closer to the global optimum in both fitness and representation space. This change means that at higher
levels the frequency of traps being set to the global optima increases, resulting in better model building and better donation quality.

@@

Gray-Box P3's progression on Ising Spin Glass, shown in Figure~\ref{fig-level-is}, is much more well behaved than on Unrestricted
NKQ. As has been typical, each application of crossover results in improved fitness, with the largest gains between the first few levels.
When approaching higher qualities these improvements also begin to translate into increased representational similarity to the global optimum.
However, as discussed previously for this problem, we again see evidence for a large number of diverse solutions with the second best
fitness. These solutions can be over 1000 bits different from the eventual best found solution. Increasing the radius of the hill climber
does not seem to significantly overcome this issue.

@@

Figure~\ref{fig-level-sat} shows that Gray-Box P3 acts more similarly on MAX-SAT to Unrestricted NKQ than any of the other problems. Again there
appears to be deceptive local optima between 500 and 1000 bits away from the nearest improving solution. Again a single solution appears
to be the ancestor of all of the solutions near the best found. This suggests that similar to Unrestricted NKQ, Gray-Box P3 will have a
hard time finding the global optimum on MAX-SAT.

In general it appears that the problems which have polynomial time solutions (Deceptive Step Trap, Nearest Neighbor NKQ, 2D Ising Spin Glass)
share a similar behavior of selection leading to the global optimum. However, the NP-Hard problems (Unrestricted NKQ, MAX-SAT) seem to contain
large amounts of higher order deception, making them challenging for selection based methods. This relationship warrants further investigation
into other NP-Hard problems to determine if the repeated selection found in P3 and other evolutionary computation methods are able to overcome
this deception. One potential avenue for improvement to P3 may also be a method for dealing with this issue. For instance, it may be beneficial to
explicitly partition solutions when this deceptive behavior is observed.
